ODGI: scalable tools for working with pangenome graphs

### 2021-05-29 manuscript/main.tex
fixed non-ASCII character

    ODGI is entirely focused on “first-order” operations on the graph (Table~\ref{tab:01}), providing, unlike VG, no
    method to construct graphs from raw sequences, map reads, or call variants. It supports interrogation of the graph
    for basic dimensional properties, positional and path-related queries, and visualization in one-dimension (1D) and
    two-dimensions (2D). ODGI also supports operations on the graph such as subset, subdivide, break, combine,
    normalize, or order its components, nodes, and paths. Most of the tools are designed to be applied together,
    piping the output of one tool into the next, thereby preventing the creation of intermediate files, and reducing
    the number of IO operations.

@@

    In the variation graph model, paths have to respect the graph’s topology: this can be verified with
    \texttt{odgi validate}, to ensure no errors in the input or edited graphs.

>>>>

    ODGI is entirely focused on "first-order" operations on the graph (Table~\ref{tab:01}), providing, unlike VG, no
    method to construct graphs from raw sequences, map reads, or call variants. It supports interrogation of the graph
    for basic dimensional properties, positional and path-related queries, and visualization in one-dimension (1D) and
    two-dimensions (2D). ODGI also supports operations on the graph such as subset, subdivide, break, combine,
    normalize, or order its components, nodes, and paths. Most of the tools are designed to be applied together,
    piping the output of one tool into the next, thereby preventing the creation of intermediate files, and reducing
    the number of IO operations.

@@

    In the variation graph model, paths have to respect the graph's topology: this can be verified with
    \texttt{odgi validate}, to ensure no errors in the input or edited graphs.
